Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-23 methods_paper/fabl-paper.tex
update.

\section{The Fellegi Sunter Approach to Record Linkage}

I think this should be reviewed so that the paper is more clear.

>>>>

\section{Review of the Fellegi Sunter Method}
In this section, we review notation, terminology, and the classical approach of Fellegi and Sunter.

I think this should be reviewed so that the paper is more clear. Consider ordered record pairs $\bm{X}_1 \times \bm{X}_2.$ 
Denote the set of matches by $\bm{M} = \{(i,j): i \in \bm{X}_1, j \in \bm{X}_2, \Delta_{ij} = 1\}.$ Denote the set of non-matches 
$\bm{U} =  \{(i,j): i \in \bm{X}_1, j \in \bm{X}_2, \Delta_{ij} = 0\}.$ An alternative way of merging two databases and removing 
duplications can be viewed as identifying the sets of matches/non-matches, or rather $\bm{M}, \bm{U}.$ In the literature, it is well known that record pairs that are estimated as matches are known as links; record pairs that are estimated as non-matches are known as non-links. \cite{fellegi_theory_1969} proposed using all-to-all pairwise comparison of records to estimate the matches/non-matches.

\newpage
